Working Notes

### 2019-02-25 notes.rmd
update

##Background:

@@

##The Build:
	df
	  df

@@

##Next Steps:
	Df
	  Df

##Etc.:
	Using a Bibliography in this format
	Can menus have sub-pages
	Adding automatic updates to top dates
	Moving top dates

##Check These Out:
  Upload 'devtools::install_github("WFU-TLC/analyzr")'

>>>>

##Background:
	Df
	  Df

@@

##The Build:
	Df
	  Df

@@

##Next Steps:
	Still in draft stage
	  Df

##Etc.:
	Using a Bibliography in this format?
	Can menus have sub-pages?
	Adding automatic updates to top dates?
	Moving top dates?
	Fix GitHub auto-upload

##Check These Out:
  Upload 'devtools::install_github("WFU-TLC/analyzr")'
  Using Mike's Metadata packager to annotate our released dataset
  Try using ```mutate(datacolumn=str_count(utterance_clean, "\\b(um|u=m)\\b"))``` to extract a string character and count.
